
\documentclass[12pt]{article}

\usepackage{hyperref}
\usepackage{draftwatermark}
\SetWatermarkText{DRAFT}
\SetWatermarkScale{5}
\title{
The Constitution of the Oregon State University Information Technology Club
\\
(Associated Students of Information Technology, Corvallis)
}

\newcommand{\article}[1]{
\setcounter{section}{0}
\setcounter{subsection}{0}

	\section*{#1}
	\addcontentsline{toc}{section}{#1}
	
}

\newcommand{\sect}[1]{
	\subsection*{#1}
	\addcontentsline{toc}{subsection}{#1}
}

\renewcommand{\thesection}{}
\renewcommand{\thesubsection}{\arabic{subsection}}
\newcommand{\revision}{ % Use this command to place the document revision at various places in the document
\begin{center}
Revision 1
\end{center}
}


\begin{document}
\maketitle{}
%\revision{}

It is the purpose of this document to define the organization that is the Oregon State University Information Technology Club, herein reffered to as OSUITC, and to define it's structure and operation in order to meet the goals described in this document.

\clearpage{}


\tableofcontents{}

\clearpage{}

\article{Article I - Organization Name}
\paragraph{}
For legal purposes this organization shall be named The Associated Students of Information Technology, Corvallis. It may be abbreviated only as ASITC.  For inter university purposes this organization shall be known as the Oregon State University Information Technology Club. It may be abbreviated as the OSU IT Club or OSUITC or ITC. 

\article{Article II - Purpose}
\paragraph{}
It is the purpose of the OSUITC to facilitate the learning and exploratoin of all topics related to the industry of information technology. It is the purpose of this organization that in doing so the members of this organization may provide support and information to their fellow students and fellow student organizations. 

\article{Article III - Members and Membership}
\paragraph{}
Student organizations are not only operated by the students, but in most cases are also defined by it's members. In order to maintain a positive experience and a good standing with the students and the school the following sections have been declared about membership.

\subsection{Eligibility}
%\addcontentsline{toc}{subsection}{Eligibility}
\paragraph{}
All students currently enrolled at Oregon State University are eligible to join the OSUITC. Special cases may be made to allow persons not currently enrolled at Oregon State University to join the OSUITC. Membership can be achieved through the Student Involvement and Leadership club database. A link to join the club may also be published to facilitate an easier process for joining.

\paragraph{}
The OSUITC is dedicated to maintaining a non discrimination profile regardless of OSU policy. For this reason the OSUITC will not deny membership to any student on the basis of age, color, disability, gener identity or expression, genetic information, marital satus, nation origin, race, religion, creed,  sex, sexual orientation, veteran status, or any other basis. 

\subsection{Member Classes}
\paragraph{}
There are no special provisions for classes of members. All members will be known only as Members. In order for a student to become a member they must be recognized as an Oregon State University student. 


%\subsubsection{Non Member}
%\addcontentsline{toc}{subsubsection}{Non Member}
%\paragraph{}
%A Non Member is anyone who is not registered as any class of member within the organization. Certain club events shall be open to Non Members in order to allow all students a chance to p%articipate in club activities before commiting to joining the OSUITC.

%\subsubsection{Member}
%\addcontentsline{toc}{subsubsection}{Member}
%\paragraph{}
%A Member is the most basic class of membership. No payment, fee, or service requirement shall be issued for any student to become a Member. All Members are granted one vote in all votes not restricted to executive members. Members are eligible to participate in all club events. Members may be restricted in which club owned equipment they are able to use. A current and valid OSU ID card and number is rquired to become a member.

%\subsubsection{Advanced Member}
%\addcontentsline{toc}{subsubsection}{Advanced Member}
%\paragraph{}
%Advanced Members share the same rights as Members with the sole exception of the ability to access and use club owned equipment. This use includes both physical access to equipment as well as virtual access to club equipment and resources.

%\subsubsection{Non Student Member}
%\addcontentsline{toc}{subsubsection}{Non Student Member}
%\paragraph{}
%The class of Non Student Member is reserved for special cases where a person who is not currently enrolled at OSU has been granted membership. This class of member does not share the same rights as the other members. Non Student Members may present no votes in any club matters. Non Student Members may not hold any office within the organization as per OSU regulations. Non Student Members may participate in all other club events.

%\subsubsection{Executive Member}
%\addcontentsline{toc}{subsubsection}{Executive Member}
%\paragraph{}
%The class of Executive Member is granted to all members that hold an office in the organization. The class is granted on the election or appointment of the member to an office, and revoked on the absence or removal of the member from an organization office. Executive Members hold the rights of Members with a few additions. Executive Members shall have far less restrictions on access to club owned equipment and resources. Executive Members are also granted one vote in all executive votes.




%
%Combine the next two sections into one
%
\subsection{Member Dues}
Any student or former member in good standing may join this club at any time. In order to maintain the membership the member must be present at every twice yearly club meeting. Twice a year there shall be a meeting including all club members in order to discuss official club matters and vote on club decisions. Attendance shall be taken at this meeting and all members not present shall be removed from the collection of members and remain in good standing. If a member cannot be present at the twice yearly meeting they must make arrangements with a club official. If the member is not present the member waives their right to vote at that meeting.

\paragraph{}
In order for a member to gain a vote for a twice yearly meeting they must have either attended or made arrangements with a club official for the previous twice yearly meeting. 

\subsection{Member Requirements}
%\addcontentsline{tox}{subsection}{Member Requirements}
\paragraph{}
Member standing shall be reviewed every two terms at a bi-anual club meeting. All Member's not in attendance who have not made previous arrangements shall be removed from the club with no penalty for rejoining. This applies to Members and Non Student Members only. Advanced Members having paid dues are exempt from this requirement as they have already paid their dues to the club. Executive Members must attend all meetings as part of their duties to the club and are exempt from this requirement during their time as an Executive Member.

\subsection{Disciplinary Action}
\paragraph{}
Disciplinary action may be required for any member who has broken a bylaw. Any member accused of breaking a bylaw has the right to a trial by their peers. Should the member admit to guilt before an Officer of the club the Member waves their right to a trial. All trials must be presided over by at least one Officer of the club and a jury of no more than 10 and no less than 5 non executive members will be constructed by a random drawing of names. Any member who's name is drawn for a jurry must accept the summon unless it poses an extreme burden on the summoned. In order to lessen the burdon of a summons a minimum of 10 days notice must be given before a trial. The time and place of the trial must be set upon so that all members called to the jury and a presiding Officer may be present. 

\paragraph{}
In order for a jury's decision to be upheld all jurors must agree unanimously. In extreme cases the accused may petition the jury's decision.  
\\
Disciplinary action may take any or all of the forms listed here:
\begin{itemize}
\item Probation from club and club events
\item Probation from using club equipment
\item Suspension from club and club events
\item Suspension from using club equipment
\item Revoking of advanced member class
\item Removal from office
\item Barring from holding any present or future office

\end{itemize}

\subsection{Resignation}
\paragraph{}
Membership of this club has no bindings and as such a member may resign from the club at any time regardless of any duties they may hold to the club. Non Executive Members may resign at any time by contacting an administrator of the club. Resignation carries no penalties and as such any member who has resigned may join the club again at any point. In order for an Officer to honorably resign they must submit notice of resignation two weeks prior to vacating the held office. Upon return to the club they may then campaign to hold another office if they desire. If they do not submit a notice of resignation two weeks prior to vacating the office they will lose their elegibility to hold any office in the club. 

\paragraph{}
If a member has paid any dues or fees and resigns from the club there will be no refunds to the member unless not issuing a refund will cause an excessive burdon on the member. Refunds must be appealed to and approved by both the Treasurer and the Vice President.


\article{Article IV - Officers}
\paragraph{}
It is necessary for the well being and the fluid operation of this club to appoint several officers to administrate and manage the club affairs.

\subsection{The Officers}
\paragraph{}
The officers shall be one President, one Vice President, one Secretary, one Treasurer, three Directors, and two Representatives. These Officers shall be elected to uphold and enforce this Constitution and the Bylaws of this organization. They are to do it to the best of their abilities and attempting to enforce them as they were intended to be enforced. The duties of each office shall be outlined in a subsequent article. All duties not explicitly written in the subsequent article for the office shall not be required of the officer to maintain office.

\subsection{Nominations and Elections}
\paragraph{}
In order to facilitate a seamless exchange of officers it is necessary to hold elections such that the officers elected may better represent the majority of the clubs needs. The requirements and process of this exchange is outlined in the following sections.

\subsubsection{Election Timeline}
\paragraph{}
Elections must happen within one school year. This is so that any graduating members that hold office will have a replacement for the next school year. Applications must be submitted before the fall term member meeting. Debates will take place between competing candidates in fall, winter, and spring term. Voting and elections will take place at the members meeting in spring term.

\subsubsection{Applications}
\paragraph{}
Any member who wishes to run for an office must submit an application before the winter term members meeting. This is so all applicants can be introduced at the same meeting. Applicants must have nominations from at least two other members not holding an office in the club. Applications must be verified by an officer to ensure validity and that the member meets the eligibility requirements for the office they are running for. Ap

\subsubsection{Debates}
\paragraph{}
There shall be four opportunities for debates during the year. They shall take place in week 8 of fall term, weeks 2 and 8 of winter term, and week 2 of spring term. They are arranged in this manner such that they begin after the members meeting of fall term and before the members meeting of spring term so that members have time to decide on a candidate in time to vote.

\subsubsection{Election and Votes}
\paragraph{}
Voting will take place at the spring term members meeting. It shall be done electronically to ensure a prompt decision and accurate results. If desired by the members a revote can be called by if two fifths of the student members of the club call for a revote. The revote shall be done in the same manner as the original vote. If a revote is called the second decision is final an no more votes may be called. 

\subsubsection{A Tie Vote Between Two Candidates}
\paragraph{}
At some point in the life of the club there may be a tie between two candidates. In order to resolve a tie vote the following procedures must be adhered to strictly. First the two candidates must Rock Paper Scissor to pick even or odd numbers. The winner of the best two out of three Rock Paper Scissor may choose between even or odd numbers. Then a twenty sided die will be rolled by the current club president on a large open surface. If the die lands on the set that was picked then that candidate wins the election. If the die lands on the set that was not chosen then the other candidate wins the election.

\subsubsection {A Tie Vote Between Three or Four Candidates}
\paragraph{}
In the unlikely event of a three way or four way tie, the procedures are similar to that of a standard tie. Rock Paper Scissor must be played tournament style to determine first, second, and third place winners. This determines the order in which the candidates will choose a range of numbers on a twelve sided die. If it is a three way tie the candidates will choose from the ranges 1-4, 5-8, and 9-12. If it is a four way tie the ranges of numbers to be chosen from are 1-3, 4-6, 7-9, and 10-12. Afer the ranges have been chosen the current president of the club will roll a 12 sided die on a large open surface. The range that the number landed on falls in determines the winner of the election.

\subsubsection{Ties between Five or More Candidates}
\paragraph{}
Should there arrise a tie between five or more candidates an immediate revote must be called, even if a revote was already called. If the tie persists then the candidacy shall be determined by a trial of open combat between the candidates. Each candidate will receive a nerf blaster. Candidates are not allowed to touch each other in any way other than by tagging with a nerf dart. If a candidate is tagged they are out of the election. The last candidate standing shall have the office.



%\subsection{Eligibility}
%\paragraph{}
%In order to maintain the integrity of this government several eligibility restrictions shall be made for the various offices. Members may only run for one office at a time. The only way for a member
%to hold multiple offices is if they are appointed to that office by the president as deemed necessary in certain situations such as an unexpected office vacancy.

\subsection{The Office of the President}
\subsubsection{Purpose and Duties}
\paragraph{}
It is the purpose of the President to oversee the club in it's entirety. To Guide the club and other officers towards the goals of the club as well as to oversee in setting those goals. The President shall
also be in charge of all decision making unless a process for a decision is specifically outlined in the constitution or the bylaws. The president may also delegate some decisions to other officers unless
restricted by the constitution or bylaws.
\subsubsection{Eligibility}
\paragraph{}
In order for a Member to be eligible to fill the office of the President there are requirements that must be met. First and foremost the office of president cannot be held by any Non-Member or Non-Student Member as required by OSU policy for student organizations. Given that the Member is not of the previously mentioned classes the member must also have maintained the status of Member for no less than one year. 

\subsection{The Office of the Vice President}
\subsubsection{Purpose and Duties}
\paragraph{}
It is the purpose of the Vice President to assist the President. In assisting the President, the Vice President may be delegated tasks by the President. The Vice President also exists to serve as the 
President in circumstances when the President may be unable to perform their duties to the club.
\subsubsection{Eligibility}
\paragraph{}
Eligibility for the Office of the Vice President shall be the same as those of the Office of the President.

\subsection{The Office of the Secretary}
\subsubsection{Purpose and Duties}
\paragraph{}
It is the purpose of the Secretary to serve both the President, the other officers, as well as the club itself. The Secretary exists to handle the logistics of even planning. The Secretary also exists
to take the minutes at all official club meetings as necessary as well as maintain accurate records of critical information regarding and serving the club.
\subsubsection{Eligibility}
\paragraph{}
In order to be eligible for the Office of the Secretary the person must be both a member of the club and a student of Oregon State University as per university regulations regarding student organizations.

\subsection{The Office of the Treasurer}
\subsubsection{Purpose and Duties}
\paragraph{}
It is the purpose of the Treasurer to oversee and maintain the finances of the club. The Treasurer exists to keep accurate and current records regarding club funds as well as expenditures from the treasury.
The Treasurer should also be able to provide and assist in financial planning and budgeting for the club and any club needs regarding funds.
\subsubsection{Eligibility}
\paragraph{}
In order to be eligible for the Office of the Treasurer the person must be both a member of the club and a student of Oregon State University as per university regulations regarding student organizations.
The Office of the Treasurer may also be subject to a background investigation as the officer will be responsible for handling and managing money.

\subsection{The Office of the Director}
\subsubsection{Purpose and Duties}
\paragraph{}
It is the purpose of the Director to oversee and handle relations regarding club members and other clubs. The Director shall also be responsible for overseeing proper use and retention of club property as 
part of member relations to the club. 
\subsubsection{Eligibility}
\paragraph{}
In order to be eligible for the Office of the Treasurer the person must be both a member of the club and a student of Oregon State University as per university regulations regarding student organizations.

\subsection{The Office of the Representative}
\subsubsection{Purpose and Duties}
\paragraph{}
It is the purpose of the Representative to assist the Director in maintaining their responsibilities. The Representatives shall also act as representatives of the club as needed by the club. They shall show
the utmost respect to any entity they will represent the club too as well as showing create taste and class. They shall keep accurate and current knowledge of the club's functions and capabilities as well
as services offered to outside entities.
\subsubsection{Eligibility}
\paragraph{}
In order to be eligible for the Office of the Treasurer the person must be both a member of the club and a student of Oregon State University as per university regulations regarding student organizations.



\article{Article V - Advisors}
\paragraph{}
In order to to fulful the requirements for a sponsored student organization there must be an advisor present from each college that provides sponsorship to this organization. The advisor will serve as a resource to the club when advice and guidance in club matters are needed. These requirements will likely change after formally requesting sponsorship from a college.

\article{Article VI - Meetings}
\paragraph{}
In order to maintain the club it may be necessary to hold frequent or infrequent meetings. This article shall cover the meetings that must happen for the club to function, as well as requirements for meetings that are not outlined in this document.

\subsection{Twice Yearly Member Meetings}
\paragraph{}
Twice a year there shall be an all member meeting in which members are required to attend to gain voting rights. These meetings must happen in week four of both fall and spring term. The time and place of the meeting must be published by club officials by the end of week two of the given term. If the time and place of the meeting is not given by week two, then the meeting defaults to the Saturday directly following week four at the time of 5 p.m. Pacific Standard Time. A default meeting location must be determined in the bylaws.

\subsection{Executive Meetings}
\paragraph{}
The officers of the club as well as the club advisors must meet the second saturday of each month to discuss official club business.

\subsection{Other Meetings}
\paragraph{}
There may arise occasions which require a club meeting that is not outlined in this document. For that case notice of the meeting must be posted no less than one week (seven days) prior to the date of meeting. The meeting must be communicated across all channels to ensure all members are aware of the meeting. Official meetings may only be called by club officers. Any member who wishes to declare an official meeting must consult an officer about it.

\article{Article VII - Removal From Office/Revoking Membership }
\paragraph{}
At some point the occasion may arise where an officer must be removed from office, or a member's membership to the club must be revoked. 

\article{Article VIII - Amendments}
\paragraph{}
As the club grows it may be possible to amend this Constitution. 

\article{Article IX - Parliamentary Authority }



\end{document}
