\documentclass[12pt]{article}

\usepackage[margin=1.0in]{geometry}

\title{
\textbf{Project Constellation Proposal}
\\
\textit{Information Technology Club, OSU}
}
\author{Zachery Thompson}
\begin{document}

\maketitle{}
\clearpage{}

\begin{center}
\LARGE{Constellation}\footnote{Citing Dictionary.com on the definition of Constellation with an added example for the third entry.}
\\
\large{$[$kon-st\textit{uh}-\textbf{ley}-sh\textit{uh} n$]$}
\\
\end{center}
noun
\begin{enumerate}
    \item \textit{Astronomy.}
    \begin{enumerate}
        \item any of various groups of stars to which definite names have been given, as Ursa Major, Ursa Minor, Bo\"{o}tes, Cancer, Orion.
        \item the section of the heavens occupied by such a group.
    \end{enumerate}
    \item \textit{Astrology.}
    \begin{enumerate}
        \item the grouping or relative position of the stars as supposed to influence events, especially at a person's birth.
        \item \textit{Obsolete.} character as presumed to be determined by the stars.
    \end{enumerate}
    \item a group or configuration of ideas, feelings, characteristics, objects, etc., that are related in some way.
    \item \textbf{\textit{any brilliant, outstanding group or assemblage}}
\end{enumerate}
\clearpage{}

\section{Where why and how}

\subsection{Where}

Not quite sure yet, check back later.

\subsection{Why}

The internet as we know it is massive, so massive in fact that seems to find its way into our every day lives in too many ways to count. The world wide web is
a large and complex web of networks that facilitates many many services to many many people. The broadness of the internet means that there are multiple industries
involved in stringing it together, and pretty much all of them are involved in using it. So why us, and why model the internet? 

The why is pretty simple. A functional model of the internet can serve as a learning end exploration platform for many topics in IT. This platform has the advantage 
of being incredibly flexible and adaptable to nearly all facets of IT. It takes a lot of equipment, technology, software, people, and cooperation to run the internet. 
This provides an opportunity for our students to  

\end{document}
