
\documentclass[12pt]{article}

\usepackage{hyperref}
\usepackage{draftwatermark}
\SetWatermarkText{DRAFT}
\SetWatermarkScale{5}
\title{
The Constitution of the Oregon State University Information Technology Club
\\
(Associated Students of Information Technology, Corvallis)
}

\newcommand{\article}[1]{
\setcounter{section}{0}
	\section*{#1}
	\addcontentsline{toc}{section}{#1}
	
}

\newcommand{\sect}[1]{
	\subsection*{#1}
	\addcontentsline{toc}{subsection}{#1}
}

\renewcommand{\thesection}{}
\renewcommand{\thesubsection}{\arabic{subsection}}
\newcommand{\revision}{ % Use this command to place the document revision at various places in the document
\begin{center}
Revision 1
\end{center}
}


\begin{document}
\maketitle{}
%\revision{}

It is the purpose of this document to define the organization that is the Oregon State University Information Technology Club, herein reffered to as OSUITC, and to define it's structure and operation in order to meet the goals described in this document.

\clearpage{}


\tableofcontents{}

\clearpage{}

\article{Article I - Organization Name}
\paragraph{}
For legal purposes this organization shall be named The Associated Students of Information Technology, Corvallis. It may be abbreviated only as ASITC.  For inter university purposes this organization shall be known as the Oregon State University Information Technology Club. It may be abbreviated as the OSU IT Club or OSUITC or ITC. 

\article{Article II - Purpose}
\paragraph{}
It is the purpose of the OSUITC to facilitate the learning and exploratoin of all topics related to the industry of information technology. It is the purpose of this organization that in doing so the members of this organization may provide support and information to their fellow students and fellow student organizations. 

\article{Article III - Members and Membership}
\paragraph{}
Student organizations are not only operated by the students, but in most cases are also defined by it's members. In order to maintain a positive experience and a good standing with the students and the school the following sections have been declared about membership.

\subsection{Eligibility}
%\addcontentsline{toc}{subsection}{Eligibility}
\paragraph{}
All students currently enrolled at Oregon State University are eligible to join the OSUITC. Special cases may be made to allow persons not currently enrolled at Oregon State University to join the OSUITC. Membership can be achieved through the Student Involvement and Leadership club database. A link to join the club may also be published to facilitate an easier process for joining.

\paragraph{}
The OSUITC is dedicated to maintaining a non discrimination profile regardless of OSU policy. For this reason the OSUITC will not deny membership to any student on the basis of age, color, disability, gener identity or expression, genetic information, marital satus, nation origin, race, religion, creed,  sex, sexual orientation, veteran status, or any other basis. 

\subsection{Member Classes}
\paragraph{}
There are no special provisions for classes of members. All members will be known only as Members. In order for a student to become a member they must be recognized as an Oregon State University student. 


%\subsubsection{Non Member}
%\addcontentsline{toc}{subsubsection}{Non Member}
%\paragraph{}
%A Non Member is anyone who is not registered as any class of member within the organization. Certain club events shall be open to Non Members in order to allow all students a chance to p%articipate in club activities before commiting to joining the OSUITC.

%\subsubsection{Member}
%\addcontentsline{toc}{subsubsection}{Member}
%\paragraph{}
%A Member is the most basic class of membership. No payment, fee, or service requirement shall be issued for any student to become a Member. All Members are granted one vote in all votes not restricted to executive members. Members are eligible to participate in all club events. Members may be restricted in which club owned equipment they are able to use. A current and valid OSU ID card and number is rquired to become a member.

%\subsubsection{Advanced Member}
%\addcontentsline{toc}{subsubsection}{Advanced Member}
%\paragraph{}
%Advanced Members share the same rights as Members with the sole exception of the ability to access and use club owned equipment. This use includes both physical access to equipment as well as virtual access to club equipment and resources.

%\subsubsection{Non Student Member}
%\addcontentsline{toc}{subsubsection}{Non Student Member}
%\paragraph{}
%The class of Non Student Member is reserved for special cases where a person who is not currently enrolled at OSU has been granted membership. This class of member does not share the same rights as the other members. Non Student Members may present no votes in any club matters. Non Student Members may not hold any office within the organization as per OSU regulations. Non Student Members may participate in all other club events.

%\subsubsection{Executive Member}
%\addcontentsline{toc}{subsubsection}{Executive Member}
%\paragraph{}
%The class of Executive Member is granted to all members that hold an office in the organization. The class is granted on the election or appointment of the member to an office, and revoked on the absence or removal of the member from an organization office. Executive Members hold the rights of Members with a few additions. Executive Members shall have far less restrictions on access to club owned equipment and resources. Executive Members are also granted one vote in all executive votes.




%
%Combine the next two sections into one
%
\subsection{Member Dues}
Any student or former member in good standing may join this club at any time. In order to maintain the membership the member must be present at every twice yearly club meeting. Twice a year there shall be a meeting including all club members in order to discuss official club matters and vote on club decisions. Attendance shall be taken at this meeting and all members not present shall be removed from the collection of members and remain in good standing. If a member cannot be present at the twice yearly meeting they must make arrangements with a club official. If the member is not present the member waives their right to vote at that meeting.

\paragraph{}
In order for a member to gain a vote for a twice yearly meeting they must have either attended or made arrangements with a club official for the previous twice yearly meeting. 

\subsection{Member Requirements}
%\addcontentsline{tox}{subsection}{Member Requirements}
\paragraph{}
Member standing shall be reviewed every two terms at a bi-anual club meeting. All Member's not in attendance who have not made previous arrangements shall be removed from the club with no penalty for rejoining. This applies to Members and Non Student Members only. Advanced Members having paid dues are exempt from this requirement as they have already paid their dues to the club. Executive Members must attend all meetings as part of their duties to the club and are exempt from this requirement during their time as an Executive Member.

\subsection{Disciplinary Action}
\paragraph{}
Disciplinary action may be required for any member who has broken a bylaw. Any member accused of breaking a bylaw has the right to a trial by their peers. Should the member admit to guilt before an Officer of the club the Member waves their right to a trial. All trials must be presided over by at least one Officer of the club and a jury of no more than 10 and no less than 5 non executive members will be constructed by a random drawing of names. Any member who's name is drawn for a jurry must accept the summon unless it poses an extreme burden on the summoned. In order to lessen the burdon of a summons a minimum of 10 days notice must be given before a trial. The time and place of the trial must be set upon so that all members called to the jury and a presiding Officer may be present. 

\paragraph{}
In order for a jury's decision to be upheld all jurors must agree unanimously. In extreme cases the accused may petition the jury's decision.  
\\
Disciplinary action may take any or all of the forms listed here:
\begin{itemize}
\item Probation from club and club events
\item Probation from using club equipment
\item Suspension from club and club events
\item Suspension from using club equipment
\item Revoking of advanced member class
\item Removal from office
\item Barring from holding any present or future office

\end{itemize}

\subsection{Resignation}
\paragraph{}
Membership of this club has no bindings and as such a member may resign from the club at any time regardless of any duties they may hold to the club. Non Executive Members may resign at any time by contacting an administrator of the club. Resignation carries no penalties and as such any member who has resigned may join the club again at any point. In order for an Officer to honorably resign they must submit notice of resignation two weeks prior to vacating the held office. Upon return to the club they may then campaign to hold another office if they desire. If they do not submit a notice of resignation two weeks prior to vacating the office they will lose their elegibility to hold any office in the club. 

\paragraph{}
If a member has paid any dues or fees and resigns from the club there will be no refunds to the member unless not issuing a refund will cause an excessive burdon on the member. Refunds must be appealed to and approved by both the Treasurer and the Vice President.


\article{Article IV - Officers}
\paragraph{}
It is necessary for the well being and the fluid operation of this club to appoint several officers to administrate and manage the club affairs.

\subsection{The Officers}
\paragraph{}
The officers shall be one President, one Vice President, one Secretary, one Treasurer, three Directors, and two Representatives. These Officers shall be elected to uphold and enforce this Constitution and the Bylaws of this organization. They are to do it to the best of their abilities and attempting to enforce them as they were intended to be enforced. The duties of each office shall be outlined in a subsequent article. All duties not explicitly written in the subsequent article for the office shall not be required of the officer to maintain office.

\subsection{Nominations and Elections}
\paragraph{}




\subsection{Eligibility}
\paragraph{}
In order to maintain the integrity of this government several eligibility restrictions shall be made for the various offices.

\subsubsection{The Office of the President}
\paragraph{}
In order for a Member to be eligible to fill the office of the President there are requirements that must be met. First and foremost the office of president cannot be held by any Non-Member or Non-Student Member as required by OSU policy for student organizations. Given that the Member is not of the previously mentioned classes the member must also have maintained the status of Member for no less than one year. 

\subsubsection{The Office of the Vice President}
\paragraph{}

\subsubsection{The Office of the Secretary}
\paragraph{}

\subsubsection{The Office of the Treasurer}
\paragraph{}

\subsubsection{The Office of the Director}
\paragraph{}

\subsubsection{The Office of the Representative}
\paragraph{}








\end{document}